Representing Scenes as Light Fields for Real Time Rendering in Virtual Reality Display

### 2021-01-12 TOG/0-abstract.tex
Updates from Overleaf

\begin{abstract}
Streaming-based graphics has revolutionized the entertainment industry. It transfers the computational pressure from individual personal computers to clustered servers. This unifies development/consumption experience and reduces local storage.
Virtual and augmented realities are the future medium that would significantly benefit from the cloud computing via reliving their currently bulky wires, demands for high-end personal computers, and consequently, low resolution/field-of-view. 
However, the current off-the-shelf streaming solutions apply only to console-based platforms due to their lower requirement of latency and quality, thus transmission performance.

Tailored for the future cloud-based virtual reality, we present the first gaze-contingent 3D neural representation and view synthesis method. Our method considers both visual acuity and neural representation for 6DoF immersive interaction. Both objective analysis and subjective studies evidenced our effectiveness of significantly reducing local storage (\warning{xxx MB} for any high quality 3D scene), transmission latency (\warning{xxx ms}), and rendering time (\warning{xxx ms}).
\end{abstract}

>>>>

\begin{abstract}
%Streaming-based graphics has revolutionized the entertainment industry. It transfers the computational pressure from individual personal computers to clustered servers. This unifies development/consumption experience and reduces local storage.
%Virtual and augmented realities are the future medium that would significantly benefit from the cloud computing via reliving their currently bulky wires, demands for high-end personal computers, and consequently, low resolution/field-of-view. 
%However, the current off-the-shelf streaming solutions apply only to console-based platforms due to their lower requirement of latency and quality, thus transmission performance.

Traditional high-quality 3D graphics requires large volume of detailed data to be rendering. This compromises efficiency and local storage. In recent years, cloud-based streaming and neural representations have significantly revolutionized the pipeline by redistributing and compressing the computation/storage. However, they typically suffer from high latency and low quality for practically large virtual scenes with 6 degree-of-freedom camera motions. These problems are particularly exacerbated in immersive medias such as virtual and augmented reality due to the demand of high frequency and resolution.

Tailored for the future cloud-based, portable, and low-storage VR platforms, we present the first gaze-contingent 3D neural representation and view synthesis approach. Our method mutually bridges both visual acuity and neural representation for 6DoF immersive interaction. Moreoever, it optimizes between temporal computational latency and spatial predictive precision. Both objective analysis and subjective studies evidenced our effectiveness of significantly reducing local storage (\warning{xxx MB, xx\% size reduction} for large 3D scenes) while preserves original perceptual quality without introducing additional latency.
\end{abstract}

### 2021-01-12 TOG/1-introduction.tex
Updates from Overleaf

Writing research documents, such as conference/journal/white papers, patent applications, grant proposals, and course reports, is a core activity for many poor souls including professors, researchers, engineers, and students.
Since we must do it one way or another, sooner or later, we might as well do it as happily and effectively as possible.
Here are my personal practices and experiences, which I have repeatedly shared with my collaborators and students throughout all these years\note{~to the point that I finally decided to write up to save the troubles}.

\note{
What prior works have done, and why they are not adequate.
(Note: this is just high level big ideas. Details should go to a previous work section.)
}%note

Some people, including very successful ones, write papers only at the end of a project, like days if not hours prior to a submission deadline.
This almost always leads to total chaos and breakdown, unless you have other means to keep track and organize all the relevant pieces of information.

@@

This document provides a template for writing research papers, and describes how to manage project progress via iterating drafts.
Doing this correctly can help you achieve productive research and happy life, e.g. working anywhere anytime without synchronous meetings with your collaborators.

@@

I learned from my PhD adviser to start writing from the moment I have the faintest idea, and gradually update the drafts to reflect progress.
During my first job with NVIDIA, I learned why and how revision control is essential for sharing and editing source files, especially among large engineering teams.
The iterative nature of writing and coding matches well with the capability of revision control.
Thus I prefer Latex + git/svn (e.g. github, bitbucket, and the svn server under my hosting service), even though I can still manage with MS Word + cloud drive (e.g. Google drive, Box, and Dropbox). 
A good computer scientist writes papers like programs, and manages Latex files like source codes.
These repos are external memories and communication mediums for the collective brains of my teams.

@@

\input{TOG/example_fig}

Translating thoughts into words, diagrams, equations, pseudo-codes, or codes is a good way to clarify and consolidate.
If you are writing a graphics/HCI paper, design the figures so that they alone can provide a high level picture of the main points.
As exemplified in \Cref{fig:example}, a figure can contain images, drawings, or combinations.

@@

You can use the associated files as a starting template for your research papers.
Start with the \filename{Makefile}, and notice the two build targets: final for official submission and public disclosure, and draft for internal sharing among your collaborators (including yourself).

>>>>

With the advent of remote desktops and streaming services, cloud-based computing has shown unprecedented potential reshaping traditional computer graphics pipeline by completely relieving end-user's computational workload, local storage volume, thus advance device portability. Recent years has seen growing interactive streaming services such as Google Stadia or NVIDIA Shield. 
However, these off-the-shelf services have only been deployed in less latency-sensitive platforms such as TV-based game consoles, due to the inevitable latency (more than 100ms \footnote{\url{https://www.pcgamer.com/heres-how-stadias-input-lag-compares-to-native-pc-gaming/}}. Immersive media such as virtual and augmented reality (VR/AR), however, demand remarkably lower latency and higher fidelity/speed for sickness-free and natural experience. 
Due to the consequently massive spatial-temporal high-quality data volume, there is no available solution today that is capable of streaming such dense content to the individual end user.

\note{
What prior works have done, and why they are not adequate.
(Note: this is just high level big ideas. Details should go to a previous work section.)
}%note
\qisun{(Jan 5, 2021) We should include two main fields: neural representation and foveated rendering}

Recent years have seen a surge in neural representations as an alternative to compact 3D representations such as point clouds and polygonal meshes, enabling compact assets. Application of neural representations include voxelization \cite{sitzmann2019deepvoxels}, distance fields \cite{sitzmann2019metasdf,mildenhall2020nerf} and many more. However, existing solutions suffer from either high time consumption or low image fidelity.

To accelerate real-time rendering tailored for VR, gaze-contingent foveated rendering approaches have shown remarkable effectiveness of presenting imagery of perceptual quality identical to full resolution rendering~\cite{Patney:2016:TFR}. This is achieved by harnessing high FoV head-mounted displays and high precision eye-tracking technologies. Unfortunately, foveated rendering approaches still require full local 3D asset storage, resulting in a significant loading time and memory shortage.

@@

In this paper, we present the first gaze-contingent real-time 6DoF neural synthesis of scenes, aiming at the next generation cloud-based wearable immersive platforms.
Specifically, our method significantly reduces 3D data storage (\warning{xxx ms}), and rendering time (\warning{xxx ms}) compared with the existing methods. It enables low-latency interactive VR/AR 6DoF viewable 3D virtual content without compromising perceived quality. Tailoring for future light weight, power and memory efficient wearable display systems, expected to be active all-day long akin to today's everyday-use mobile phones, our method achieves minimal local storage for any high quality 3D scenes.

@@

In this work, we take an interdisciplinary approach achieving 6-DoF deep neural representation of complex scenes and gaze-contingent real-time rendering. This is realized by our novel data representation and a coarse-to-fine prediction of perceptually high quality imagery while balancing the latency.

@@

Specifically, we represent an arbitrary virtual 3D scene as a compact neural representation in a viewer centered inside-out fashion. 
We account for the challenges such as low quality/resolution/performance common to existing 3D deep neural representation approaches, we further leverage the human visual perception to synthesize gaze-contingent and vision-matched immersive frames, without compromising the speed and image fidelity. 
The method is further optimized with in the spatio-temporal domain to balance the latency and precision.

@@

We validate our approach by conducting both numerical analysis and user evaluations on commercially available AR/VR display devices. They both reveal the effectiveness of our method on delivering a real-time VR viewing experience, perceptually identical to an arbitrarily high quality rendered 3D scene, without compromising on local storage volume. Our main contributions include the following:
\begin{itemize}
    \item A low-latency and significantly low-storage 6DoF immersive application that preserves perceptual quality
    \item A gaze-contingent neural representation and synthesis method tailored for first-person viewing
    \item A spatio-temporally joint optimization for balancing latency and perceptual quality
\end{itemize}

### 2021-01-12 TOG/title_author.tex
v0.01: title, abstract, submission ID
Updates from Overleaf

\title{Using Paper Drafts to Manage Research Projects}

>>>>

\title{Representing Scenes as Light Fields for Real Time Rendering in Virtual Reality Display}
\title{Immersive 6DoF Streaming with Gaze-Contingent Neural Synthesis} 
\title{Gaze-Contingent Neural Synthesis for Low Latency VR in-the-Cloud} 
\title{GazeNet: Gaze-Contingent Neural Synthesis for Low Storage VR} 
% Representing Scenes as Neural Radiance Fields for View Synthesis

% perceptually-aware neural synthesis for low latency 6dof VR?
% perceptual neural rendering for ultra fast 6dof VR
